### 2022-09-01 main/chapter_searches.tex
add fisher quote on communicating likelihoods

>>>>

\begin{singlespacing}
\begin{displayquote}
For all purposes, and more particularly for the \textit{communication} of the
relevant evidence supplied by a body of data, the values of the Mathematical
Likelihood are better fitted to analyse, summarize, and communicate
statistical evidence of types too weak to supply true probability statements
\end{displayquote}
\end{singlespacing}
~\cite{fisher1956statistical}
